---
title: "HW1_Macro-finance"
author: "Shayan Abbasi"
date: "4/11/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



## Cleaning the environment

First of all we clear the environment and install and load the libraries:

```{r}
rm(list = ls()) 
rm(list = ls(all.names = TRUE))
```

## Check Libraries

```{r}
if (!require('plotly')) install.packages('plotly'); library(plotly)
if (!require("dplyr")) install.packages("dplyr"); library(dplyr)
if (!require("knitr")) install.packages("knitr"); library(knitr)
if (!require("readxl")) install.packages("readxl"); library(readxl)
```

More insight on the data: https://www.macrohistory.net/app/download/9834516469/RORE_documentation.pdf?t=1614633099

#Import Data
```{r}
data <- read_excel("JSTdatasetR5.xlsx", sheet = "Data")
data
```

#Crisis: 


#Real stock price index



#Real house price index



#Real GDP index











#Citation
  1. Òscar Jordà, Katharina Knoll, Dmitry Kuvshinov, Moritz Schularick, and Alan M. Taylor. 2019. “The Rate of Return on Everything, 1870–2015.” Quarterly Journal of Economics, 134(3), 1225-1298.
  [Source Data] https://www.macrohistory.net/database/